### 2020-07-20 article.tex
Again, MATSBAIJMKL is not a PETSc keyword...

The CPU configuration which reaches the
highest percentage of peak is \pk{MATSBAIJMKL}~\ref{pgfplots:sbaijmkl3} with $b=3$
and $N=64$, rightmost middle plot in~\cref{fig:perfAXpar}, with approximately
63 GFLOP/s. This format is not available yet in PETSc, but it is handled by the
mini-app. Still, it is less than 1\% of peak for an Intel Xeon Gold 6248.
For the GPU configuration, \pk{MATAIJCUSPARSE}~\ref{pgfplots:cusparse10} with $b=6$
and $N=64$, rightmost bottom plot in~\cref{fig:perfAXpar}, performs at around
306 GFLOP/s, about 4\% of peak for an NVIDIA Tesla V100 SXM2. These rather disappointing performances
suggest to consider different, interlaced layouts for storing the dense right-hand sides and we plan to extend the
current PETSc functionality in the future to maximize performances while maintaining interface flexibility
and the user friendliness of the library.
{\color{red} Pierre, can you do a quick run hacking MatProduct.cpp and using MAIJ MatMult instead of MatProductNumeric just to confirm this
sentence and add preliminary numbers in terms of CPU peak performance? (forget about GPU, we need a new interface to CUSPARSE for that)}

>>>>

The CPU configuration which reaches the
highest percentage of peak is MATSBAIJMKL~\ref{pgfplots:sbaijmkl3} with $b=3$
and $N=64$, rightmost middle plot in~\cref{fig:perfAXpar}, with approximately
63 GFLOP/s. This format is not available yet in PETSc, but it is handled by the
mini-app. Still, it is less than 1\% of peak for an Intel Xeon Gold 6248.
For the GPU configuration, \pk{MATAIJCUSPARSE}~\ref{pgfplots:cusparse10} with $b=6$
and $N=64$, rightmost bottom plot in~\cref{fig:perfAXpar}, performs at around
306 GFLOP/s, about 4\% of peak for an NVIDIA Tesla V100 SXM2. These rather disappointing performances
suggest to consider different, interlaced layouts for storing the dense right-hand sides and we plan to extend the
current PETSc functionality in the future to maximize performances while maintaining interface flexibility
and the user friendliness of the library.
{\color{red} Pierre, can you do a quick run hacking MatProduct.cpp and using MAIJ MatMult instead of MatProductNumeric just to confirm this
sentence and add preliminary numbers in terms of CPU peak performance? (forget about GPU, we need a new interface to CUSPARSE for that)}
